### 2020-05-08 README.Rmd
fixed forward and backslashes on html code block

System        | .Renviron file locations
--------------|-------------------------
MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
Linux / MacOs | `/home/<username>/.Renviron`

>>>>

System        | .Renviron file locations
--------------|-------------------------
MS Windows    | <code>C:&#92;Users&#92;&#8249;username&#8250;&#92;.Renviron</code>  or <code>C:&#92;Users&#92;&#8249;username&#8250;&#92;Documents&#92;.Renviron</code>
Linux / MacOs | <code>&#47;home&#47;&#8249;username&#8250;&#47;.Renviron</code>
